ZCB Pricing

### 2018-07-02 ZCB Pricing .Rmd
I have uploaded another verion of the MOnte Carlo simulations as well. This makes use of the Euler discretization. It turns out that the Euler and Milstein discretization is the same.
The variance reduction methods have also been uploaded

```{r 3}
# Improvements to the Monte Carlo Simulation
# Antithetic Variates

>>>>

```{r}
#Generate normal RV
z=rnorm(1000)
z.=-z

# Another Version of the MOnte Carlo simulations
Crude_Monte_Carlo=function(alpha,beta,sigma,T,r0,n,s){

  # alpha, beta, sigma <- Fixed Parameters
  # T <- maturity time
  # r0 <- Initial rate at time 0
  # n <- Number of Simulations
  # s <- NUmber of Subintervals

  #Simulate interest rates
  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r0

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*rnorm(1)# Euler Discretization
      sim_path[j,i]=sim_path[j-1,i]+dr
    }
  }

  # Monte Carlo Simulations
  Sum=colSums(sim_path[2:(s+1),]*dt)
  int=exp(-Sum)
  mean=mean(int)
  sd=sd(int)/sqrt(n)
  result=c(mean,sd)
  result
}
```

```{r 3}
# Improvements to the Monte Carlo Simulation

#################################################################################
# Antithetic Variates
################################################################################

Antithetic_variates= function(alpha,beta,sigma,T,r0,n,s){
  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path_inv= matrix(0,nrow = s+1, ncol = n)# matrix to generate interest paths using inverse RV
  sim_path[1,]= r0
  sim_path_inv[1,]=r0

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[j-1] # Euler Discretization
      dr_i= alpha*(beta-sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[j-1]
      sim_path[j,i]=sim_path[j-1,i]+dr
      sim_path_inv[j,i]=sim_path_inv[j-1,i]+dr_i

    }
  }

  # Monte Carlo Simulations
  Sum=colSums(sim_path[2:(s+1),]*dt)
  Sum.=colSums(sim_path_inv[2:(s+1),]*dt)
  int.=exp(-Sum.)
  int=exp(-Sum)# Estimate using the conjugate rates
  Average=(int+int.)/2 # Average of estimates
  mean=mean(Average)
  sd=sd(Average)/sqrt(n)
  result=c(mean,sd)
  result

```{r}
#################################################################################
# Moment matching
#################################################################################

Moment_Matching=function(alpha,beta,sigma,T,r0,n,s){

  # alpha, beta, sigma <- Fixed Parameters
  # T <- maturity time
  # r0 <- Initial rate at time 0
  # n <- Number of Simulations
  # s <- NUmber of Subintervals

  #Simulate interest rates
  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r0
  z=rnorm(s)
  z_m= z-mean(z) # MOMENT MATCHING TRANSFORMATION

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[j-1]# Euler Discretization
      sim_path[j,i]=sim_path[j-1,i]+dr
    }
  }

  # Monte Carlo Simulations
  Sum=colSums(sim_path[2:(s+1),]*dt)
  int=exp(-Sum)
  mean=mean(int)
  sd=sd(int)/sqrt(n)
  result=c(mean,sd)
  result
}
```

```{r}
#################################################################################
# Control Variates
#################################################################################

# We have decided to make use of the CIR model as our control variate process.
# Below is the closed form solution under the CIR model
bond_price_CIR <- function(alpha,beta,sigma,t,T,r0){
  h <- sqrt(alpha^(2)+2*sigma^(2))
  A <-(2*h*exp((alpha+h)*(T-t)/2)/(2*h+(alpha+h)*(exp((T-t)*(h))-1)))^((2*alpha*beta)/sigma^(2))
  B <-2*(exp((T-t)*(h))-1)/(2*h+(alpha+h)*(exp((T-t)*(h))-1))
  A*exp(-B*r0)
}

# Monte Carlo Simulations of Bond Price under the CIR model

CIR_MC= function(alpha,beta,sigma,T,r0,n,s){

  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r0

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=alpha*(beta-sim_path[j-1,i])*dt+(sigma*sqrt(dt)*rnorm(1)*sqrt(sim_path[j-1,i]))# Euler Discretization
      sim_path[j,i]=sim_path[j-1,i]+dr

    }
  }

  # Monte Carlo Simulations
  Sum=colSums(sim_path[2:(s+1),]*dt)
  int=exp(-Sum)
  mean=mean(int)
  sd=sd(int)/sqrt(n)
  result=c(mean,sd)
  result

# Therefore the control variates estimate:

Control_Variates_estimate= function(alpha, beta, sigma,t,T,r0,n,s){
  Crude_Monte_Carlo(alpha,beta,sigma,T,r0,n,s)[1]- CIR_MC(alpha,beta,sigma,T,r0,n,s)[1]+bond_price_CIR(alpha,beta,sigma,t,T,r0)
}
